---
title: "#notdying4wallstreet Sentiment Analysis & User/Hashtag Analysis"
author: "Hana Yerin Lim"
date: "1/17/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(readxl)
library(dplyr)
library(readr)
a <- read_excel("TAGS-NotDying4WallStreet - Archive.xlsx")
b <- read_csv("TAGS-ReopenAmerica - Archive.csv")
a %>% arrange(desc(user_followers_count))
```

```{r message=FALSE, warning=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
words <- c() 
for(i in 1:626){
  words <- c(words, unique(str_extract_all(a$text, "#\\S+"))[[i]])
}
#unique(words) #735
freq_hash <- table(words) %>% as.data.frame() %>% arrange(desc(Freq))
temp <- freq_hash[-c(1,3, 13, 14), ]
top20 <- temp[1:20, ]
ggplot(top20, aes(x = reorder(words, Freq), y = Freq)) + geom_bar(stat="identity", aes(fill = Freq)) + coord_flip() + 
  scale_fill_gradient2(mid = "skyblue", high = "red", midpoint = median(top20$Freq)) + 
  ggtitle("Top 20 Hashtags Used Along #notdying4wallstreet") + 
  xlab("Frequency") + ylab("Top 20 Hashtags")


words <- c() 
for(i in 1:length(unique(str_extract_all(b$text, "#\\S+")))){
  words <- c(words, unique(str_extract_all(b$text, "#\\S+"))[[i]])
}
#unique(words) #735
freq_hash <- table(words) %>% as.data.frame() %>% arrange(desc(Freq))
temp <- freq_hash[-c(1, 9, 13, 15, 17, 23), ]
top20 <- temp[1:20, ]
ggplot(top20, aes(x = reorder(words, Freq), y = Freq)) + geom_bar(stat="identity", aes(fill = Freq)) + coord_flip() + 
  scale_fill_gradient2(mid = "skyblue", high = "red", midpoint = median(top20$Freq)) + 
  ggtitle("Top 20 Hashtags Used Along #reopenAmerica") + 
  xlab("Frequency") + ylab("Top 20 Hashtags")
```

```{r}
library(viridis)
followers <- a %>% arrange(desc(user_followers_count)) %>% distinct(from_user, .keep_all = TRUE)
# ggplot(followers[1:30, ], aes(x = reorder(from_user, user_followers_count), y = user_followers_count)) + geom_bar(stat="identity", aes(fill = user_followers_count)) + coord_flip() + 
#   scale_fill_viridis_c(option = 'viridis', direction = -1) +
#   ggtitle("Top 30 accounts with the most followers") + 
#   xlab("Accounts") + ylab("Followers Amounts")

library(treemap)
followers$label <- paste(followers$from_user, followers$user_followers_count, sep = "\n")
treemap(followers[1:20, ], index = "label", vSize = "user_followers_count", vColor = "user_followers_count", type = "value")
```

1. Ben Shapiro: American conservative political commentator and media host

2. Naomi A Klein: Canadian author, social activist, and filmmaker known for her political analyses and criticism of corporate globalization and of capitalism.

3. Eva Golinger: Venezuelan-American lawyer, writer and journalist.

4. WE are teachers: teachers based on Texas 

5. Jon Cooper: Canadian-American professional ice hockey coach

6. Matthew VanDyke: American documentary filmmaker, revolutionary, and former journalist

### Follower Friend ratio is not outputed 
```{r, eval = FALSE}
a$follower_friend_ratio <- round((a$user_followers_count/a$user_friends_count)*100, 4)
a %>% arrange(desc(follower_friend_ratio))
```

```{r}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("syuzhet")
library("ggplot2")
a_copy <- a
x <- a_copy$text
stopwords = readLines("stoplist - keywords-29a98930edd440581bf3b48c5a4e72cb.rtf.txt")
TextDoc <- Corpus(VectorSource(a_copy$text))

#Replacing "/", "@" and "|" with space
toSpace <- content_transformer(function (x , pattern) gsub(pattern, " ", x))
suppressWarnings(TextDoc <- tm_map(TextDoc, toSpace, "/"))
suppressWarnings(TextDoc <- tm_map(TextDoc, toSpace, "@"))
suppressWarnings(TextDoc <- tm_map(TextDoc, toSpace, "\\|"))
# Convert the text to lower case
suppressWarnings(TextDoc <- tm_map(TextDoc, content_transformer(tolower)))
# Remove numbers
suppressWarnings(TextDoc <- tm_map(TextDoc, removeNumbers))
# Remove english common stopwords
suppressWarnings(TextDoc <- tm_map(TextDoc, removeWords, stopwords))
# Remove your own stop word
# specify your custom stopwords as a character vector
suppressWarnings(TextDoc <- tm_map(TextDoc, removeWords, c("RT", "notdying4wallstreet", "notdyingwallstreet", "https", "amp", "’", "peopl")) )
# Remove punctuations
suppressWarnings(TextDoc <- tm_map(TextDoc, removePunctuation))
# Eliminate extra white spaces
suppressWarnings(TextDoc <- tm_map(TextDoc, stripWhitespace))
# Text stemming - which reduces words to their root form
suppressWarnings(TextDoc <- tm_map(TextDoc, stemDocument))
```

# most frequent words 
```{r}
TextDoc_dtm <- TermDocumentMatrix(TextDoc)
dtm_m <- as.matrix(TextDoc_dtm)
# Sort by descearing value of frequency
dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
dtm_d <- dtm_d[-1, ]
# Display the top 5 most frequent words
head(dtm_d, 10)
```

# word association 
```{r}
findAssocs(TextDoc_dtm, terms = c("trump", "listen", "want","die","risk","live","american"), corlimit = 0.25)			
```

# sentiment analysis
```{r}
syuzhet_vector <- get_sentiment(x, method="syuzhet")
```

```{r}
d <- get_nrc_sentiment(x)
```

```{r}
td<-data.frame(t(d))
#The function rowSums computes column sums across rows for each level of a grouping variable.
td_new <- data.frame(rowSums(td[2:9262]))
#Transformation and cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:8,]
#Plot One - count of words associated with each sentiment
quickplot(sentiment, data=td_new2, weight=sort(count, decreasing = TRUE), geom="bar", fill=sentiment, ylab="count") + ggtitle("#notdying4wallstreet Sentiments")
```

```{r}
# data from vader sentiment analysis 
data1 <- read.csv("NotDying4WallStreet.csv")
data1$Neutral <- (data1$Negative == "False") & (data1$Positive == "False")
# Counts: data1 %>% group_by(Negative, Positive, Neutral) %>% summarise(counts = n())
vader_data <- data.frame(sentiment = c("Negative", "Positive", "Neutral"), counts = c(4239, 2773, 2250), prop = c(round(4239/(4239+2773), 3)*100, round(2773/(4239+2773), 3)*100, "-"))
ggplot(vader_data, aes(sentiment, counts, fill = sentiment)) + geom_bar(stat = "identity") +
  geom_text(aes(label = counts, vjust = 1)) +
  ggtitle("Bar Chart of #notdying4wallstreet Sentiment Counts")
  
ggplot(vader_data[-3,], aes("", prop, fill = sentiment)) + geom_bar(stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  geom_text(aes(label = paste0(prop, "%")), position = position_stack(vjust = 0.5)) + 
  ggtitle("Pie Chart of #notdying4wallstreet Sentiments Proportion") + 
  theme(axis.text = element_blank(), axis.ticks = element_blank(), panel.grid  = element_blank())

ggplot(data1, aes(x = compound)) + geom_histogram(color = "white", fill = "lightblue", binwidth = 0.1) + ggtitle("Histogram of Sentiment Compound")
```

Histogram of Sentiment Compound: Negative outnumbers positive compounds 

source from: https://www.red-gate.com/simple-talk/sql/bi/text-mining-and-sentiment-analysis-with-r/